### 2023-06-02 paper/content.tex
Cite Janine's data with the DOI instead of the raw link

The Python source code used to produce all results and figures presented here
is available at \url{https://github.com/\GitHubRepository} and
\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
The QDM magnetic microscopy data are available at~\url{https://figshare.com/articles/dataset/QDM_magnetic_microscopy_dataset_of_a_speleothem_from_Morocco/22965200} under the CC-0 license.

>>>>

The Python source code used to produce all results and figures presented here
is available at \url{https://github.com/\GitHubRepository} and
\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
The QDM magnetic microscopy data are available
at~\url{https://doi.org/10.6084/m9.figshare.22965200.v1} under the CC-0 license.
